% mainfile: ../master_thesis_GW.tex
\chapter{Introduction -- calculation of the unrenormalized effective potential}

Tree level potential in our model is:
\begin{equation}
V_T = \frac{1}{4}\lambda(\varphi_1^2+\varphi_2^2)^2.
\end{equation}


The one loop correction to the effective potential is calculated as a sum of the following diagrams:
\\
\begin{align}
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\frac{1}{2n}&\left(\frac{\lambda\frac{1}{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n \\
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\frac{1}{2n}&\left(\frac{1}{3}\frac{\lambda\frac{1}
{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n \\
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\frac{1}{2n}&\left(\frac{2e^2\frac{1}{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n(g^\mu_{\ \,\mu} - 1).
\end{align}

Summing all the diagrams in series it gives:

\begin{align}
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\sum\limits_{n=1}^{\infty}
\frac{1}{2n}&\left(\frac{\lambda\frac{1}{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n \\
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\sum\limits_{n=1}^{\infty}\frac{1}{2n}&
\left(\frac{1}{3}\frac{\lambda\frac{1}{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n \\
i\int \frac{\textrm{d}^4k}{(2\pi)^4}\sum\limits_{n=1}^{\infty}\frac{1}{2n}&
\left(\frac{2e^2\frac{1}{2}\varphi_1^2}
{k^2+i\varepsilon}\right)^n(g^\mu_{\ \,\mu} - 1).
\end{align}
\label{divergent sums}
These integrals seems to be hideously infrared divergent. 
We can, however Wick rotate them to the Euklidean space and perform summation to get:
\begin{align}
logarithms
\end{align}
Now, integrals have only singularity at $\varphi_1 = 0$. \\
There are now several ways to perform the integrals. We will present here briefly two of them: 
cut-off and
dimentional regularisation (DR). \\
For all of our further calculations, we will use DR, but cut-off will apear in \ref{CWchapter} 
as a method used in \cite{Coleman1973}. \\
\section{Cut-off}
The idea of this method is to restrict the integration to $k^2 \leq \Lambda$, for a 
parameter $\Lambda$. 
%Then, with the end result calculated this way at hand, take the limit as $\Lambda \to \infty$.
\section{Dimentional regularisation}
The idea of this method is to observe, that the divergence is only in four dimentions 
and if we formally change expresions to $4-2\epsilon$ dimentions. 
It is performed by treating the integral as a linear functional depending on two parameters --
function and dimention given by some specific formula. Then we can calculate it with our 
function of interest and $D = 4-2\epsilon$ as arguments.  \\
%$D = 4-2\epsilon$
After passing to $D=4-2\epsilon$ dimensions and using dimensional regularisation we have:
\begin{align}
V_{1L}=\frac{1}{4}\frac{(\frac{1}{2}\lambda\varphi_1^2)^2}{(4\pi)^2}&\left(-\frac{2}{\epsilon}
+\gamma_E-\frac{3}{2}+\log{\frac{(\frac{1}{2}\lambda\varphi_1^2)^2}{4\pi\mu^2}}\right)  \\
+\frac{1}{4}\frac{(\frac{1}{6}\lambda\varphi_1^2)^2}{(4\pi)^2}&\left(-\frac{2}{\epsilon}
+\gamma_E-\frac{3}{2}+\log{\frac{(\frac{1}{6}\lambda\varphi_1^2)^2}{4\pi\mu^2}}\right)  \\
+\frac{1}{4}\frac{3(e^2\varphi_1^2)^2}{(4\pi)^2}&\left(-\frac{2}{\epsilon}+\gamma_E
-\frac{5}{6}+\log{\frac{e^2\varphi^2}{4\pi\mu^2}}\right)
\end{align}
\section{}
The task that is still left, is to 
